Exploring probability distributions for bivariate temporal granularities

### 2019-12-09 main.Rmd
edit till introduction

The remainder of the paper is organized as follows. \autoref{sec:lineartime} details the background of linear granularities in depth and briefly explain calendar algebra for computing different linear granularities. \autoref{sec:cyclic-gran-def} formally characterizes different cyclic time granularities by extending the framework of linear time granularities. Section \ref{sec:cyclic-calendar} introduces cyclic calendar algebra for computing cyclic time granularities. \autoref{sec:data-structure} discusses the data structure for exploring distribution of an observed variable across pair of cyclic time granularities. \autoref{sec:visualization} discusses the role of different factors in constructing an informative and trustworthy visualization. Section \ref{sec:application} examines how systematic exploration can be carried out for a temporal and non-temporal application. Section \ref{sec:discussion} summarizes this paper and discusses possible future direction.

# Linear time granularities {#sec:lineartime}

@@

## Definitions and Relationships

@@

## Computation through Calendar Algebra

@@

Some relevant grouping oriented operations are discussed, which will be used in Section \ref{sec:cyclic-gran-def} to define circular and aperiodic granularities.

@@

# Cyclic time granularities {#sec:cyclic-gran-def}

@@

In \autoref{sec:cyclic-gran-def}, we discussed how we can define cyclic granularities by extending the concept of linear granularities defined in @Bettini1998-ed. In this section, we will see how to obtain cyclic granularities through an algebraic representation of other cyclic granularities. This is similar to calendar algebra in @Ning2002-tf, where linear granularities are generated from the bottom linear granularity or from those that are already generated. Since, our method caters to computation of cyclic granularities, we shall refer to it as "cyclic calendar algebra".

@@

## Choice of Plots

>>>>

The remainder of the paper is organized as follows: \ref{sec:linear-time} details the background of linear granularities in depth and briefly explain calendar algebra for computing different linear granularities. \ref{sec:cyclic-gran} formally characterizes different cyclic time granularities by extending the framework of linear time granularities. Section \ref{sec:cyclic-calendar} introduces cyclic calendar algebra for computing cyclic time granularities. \ref{sec:data-structure} discusses the data structure for exploring distribution of the associated time series across pair of cyclic time granularities. \ref{sec:visualization} discusses the role of different factors in constructing an informative and trustworthy visualization. Section \ref{sec:application} examines how systematic exploration can be carried out for a temporal and non-temporal application. Section \ref{sec:discussion} summarizes this paper and discusses possible future direction.

# Linear time granularities {#sec:linear-time}

@@

## Definitions and relationships

@@

## Computation through calendar algebra

@@

Some relevant grouping oriented operations are discussed, which will be used in Section \ref{sec:cyclic-gran} to define circular and aperiodic granularities.

@@

# Cyclic time granularities {#sec:cyclic-gran}

@@

In \autoref{sec:cyclic-gran}, we discussed how we can define cyclic granularities by extending the concept of linear granularities defined in @Bettini1998-ed. In this section, we will see how to obtain cyclic granularities through an algebraic representation of other cyclic granularities. This is similar to calendar algebra in @Ning2002-tf, where linear granularities are generated from the bottom linear granularity or from those that are already generated. Since, our method caters to computation of cyclic granularities, we shall refer to it as "cyclic calendar algebra".

@@

## Choice of statistical distribution plots
